\chapter{Breads, Buns and Rolls}
\section{Pre-Ferment Bread}

\header{Ingredients}
For a single loaf

\ingredientsection{Pre-Ferment (Poolish)}
\begin{enumerate}
  \item 150g flour (12\%+ protein or type 650+)
  \item 150g water (room temperature)
  \item 1g fresh yeast
\end{enumerate}

\ingredientsection{Dough}
\begin{enumerate}
  \item 400g flour (12\%+ protein or type 650+)
  \item 280g water (35C)
  \item 6g fresh yeast
  \item 10g salt
\end{enumerate}

\header{Instructions}
Prepare the poolish by mixing all ingredients in a glass jar or a glass
container. Leave to ferment in room temperature for 16-24 hours.

Once the poolish is ready, mix it with the ingredients for the dough in a large
bowl until homogenous. Leave to rest for around 30 minutes, then fold several
times onto itself. Repeat at least one more time and leave to rest for 30
minutes.

Take the dough out of the bowl onto a surface lightly sprinkled with flour.
Fold the dough onto itself several times by grabbing an edge of the dough,
stretching it up and bringing it to the opposite side. Work clockwise or
counterclockwise. Flip the dough upside-down and shape into a ball to form a
smooth surface by pulling the dough under itself. Keep the seam at the bottom
of the ball throughout the process.

Prepare a proofing basket or line a large bowl with a clean kitchen towel and
toss very generously with flour (otherwise the dough will stick to the towel).
Toss the top of the dough with flour and place it seam side up in the proofing
basket. Proof at room temperature for 30 minutes to one hour.

While the dough is proofing, heat the oven and a dutch oven (you may use a
large steel pot with a lid as a replacement) to 250C. Once hot, sprinkle the
bottom of the dutch oven with flour and carefully place the dough in it. Do not
drop the dough as it will lose the gases built up during proofing resulting in
a flatter loaf. Score the top of the bread deeply. Bake covered for 20 minutes,
remove the cover and bake for 20 or more minutes to achieve dark brown crust.

\section{Sourdough Bread}

\section{Tortillas}
\header{Ingredients}
\begin{itemize}
  \item flour
  \item 60\% lukewarm water
  \item 10\% oil
  \item 2\% salt
\end{itemize}

\header{Instructions}
The recipe mentions a pan, however, any other flat metal surface, such as
gridle, is fine.
\begin{enumerate}
  \item Dissolve the salt in the water.
  \item Add oil and flour, then mix until rough dough.
  \item Leave to autolyse for 30 minutes.
  \item Knead until homogenous, then leave to rest for 10 minutes.
  \item Heat up the pan on medium heat.
  \item Divide the dough into balls.
  \item Using plenty flour, roll one ball at a time into a 1mm thick disc. Then
    place it on the pan. Once there is a visible light browning on the bottom
    side (around 30 seconds to 1 minute), flip over for about 20-30 seconds.
  \item Stack the tortillas on a plate. Once done cooking all tortillas, cover
    the plate with tin foil or anything non-permeable to trap the steam in.
\end{enumerate}

\section{Pide}
\section{Burger Bun}
This recipe makes 6 buns (150g).

\header{Ingredients}
\begin{enumerate}
  \item 125g milk (lukewarm or room temperature)
  \item 125g water (lukewarm or room temperature)
  \item 20g yeast
  \item 15g sugar
  \item 1 whole egg + 1 egg yolk
  \item 10g salt
  \item 525g flour
  \item 65g butter (softened)
  \item sesame (optional)
  \item 1 whole egg for egg wash
\end{enumerate}

\header{instructions}
\begin{enumerate}
  \item Mix together milk, water, yeast, sugar, salt and eggs.
  \item Add flour, mix, then knead for up to 5 minutes.
  \item Knead the butter into the dough and continue kneading until the dough
  does not stick anymore.
  \item Form into a ball and leave for at least an hour to rise.
  \item Divide into 6 even portions and shape into balls. Place on sheets of
  parchment paper, then lightly coat the tops of the buns with oil and gently
  flatten with the bottom of a glass.
  \item Cover the buns with cloth and leave to proof for 30 minutes to an hour.
  \item Preheat the oven to 190C.
  \item Mix together an egg and a little water (about a tablespoon), then brush
  the tops of the buns with the egg wash. Coat generously with sesame.
  \item Bake for 17-20 minutes.
\end{enumerate}

\section{Hoagie Roll}
