\chapter{Cakes}
\section{Genoise}
\section{Shortcake}

\section{Carrot Cake}
This recipe is scaled to a 15cm (diameter) cake tin.

\subsection*{Ingredients}
\begin{enumerate}
  \item 120g eggs (room temperature)
  \item 70g sugar (prefer brown for better moisture retention, but white is also
  perfect)
  \item 77g oil (odourless, e.g. canola)
  \item 110g flour
  \item 55g almond powder (substitute with flour if not available)
  \item 3g cinnamon
  \item 6.5g baking powder
  \item 2g salt
  \item 170g carrots (mass after peeling)
  \item 50g walnuts
  \item 50g raisins
\end{enumerate}

\subsection*{Instructions}
\begin{enumerate}
  \item Line the bottom and the sides of your tin with parchment paper.
  \item Preheat oven to 165C.
  \item Submerge raisins in rum/water/liquid of your choice and leave to soak.
  \item Grate carrots on the fine side of your grater.
  \item Chop walnuts.
  \item Whisk eggs and sugar.
  \item Add oil and whisk until well combined.
  \item Add dry ingredients (flour, almond powder, cinnamon, baking powder,
  salt) and mix well with a spatula.
  \item Add carrots, walnuts, drained raisins and mix.
  \item Pour into the tin. Drop the tin from about 10cm to remove large air
  bubbles in the batter.
  \item Bake 40-45 mins.
  \item Invert onto a cooling rack, remove the tin and the parchment paper.
  cool for 10 mins, then flip up-side-down and continue cooling until edible or
  room temperature.
  \item Slice into 3 layers of 1.5cm to 2cm height. Layer with cream cheese
  frosting.
\end{enumerate}

\section{Cream Cheese Frosting}

\header{Ingredients}
\begin{enumerate}
  \item 320g cream cheese (room temperature)
  \item 120g powder sugar
  \item 160g butter (room temperature)
  \item 3.5g lemon zest
  \item 30g heavy cream
\end{enumerate}

\header{Instructions}
\begin{enumerate}
 \item Mix the cream cheese with the powder sugar.
 \item In another bowl mix the the butter to soften it. This helps ensure there
 will be no clumps of butter in the frosting.
 \item Add the butter to the cream cheese and mix until homogenous.
 \item Add lemon zest and heavy cream. Mix until homogenous.
 \item Chill in the fridge for about 20 minutes before using.
\end{enumerate}

\section{Szarlotka (Apple Cake)}
\begin{enumerate}
  \item 400g flour
  \item 150g butter
  \item 2 egg yolks (about 30g)
  \item 150g cream 30\% or 36\%
  \item 8g salt
  \item 75g sugar
\end{enumerate}
