\chapter{Sides}
\section{Spring Rolls}
\subsection{Wrappers}

\header{Ingredients}
\begin{enumerate}
  \item wheat flour
  \item 50\% water
  \item 10\% oil
  \item 2\% salt
\end{enumerate}

\header{Instructions}
\begin{enumerate}
  \item Mix the ingredients into rough dough and leave to autolyse for 30
  minutes to an hour.
  \item Knead the dough lightly to ensure it is homogenous, form into a ball
  and leave to rest for 30 minutes up to overnight in the fridge.
  \item Measure out 35g portions of the dough and roll them into 1mm thick
  sheets, then cut into squares. Dust generously with flour to ensure they do
  not stick when stacked. If using a pasta machine, roll the entire dough into
  1mm thick sheet, then cut into squares.
\end{enumerate}

\subsection{Filling}
\header{Ingredients}
\begin{enumerate}
  \item 250g ground pork
  \item 1 carrot
  \item 2 leaves of napa cabbage
  \item 1/2 red bell pepper
  \item scallion
  \item 2 cloves of garlic
\end{enumerate}

\header{Marinade}
\begin{enumerate}
  \item 15ml soy sauce
  \item 5ml sesame oil
  \item 5g sugar
\end{enumerate}

\header{Sauce}
\begin{enumerate}
  \item 30ml fish sauce
  \item 30ml oyster sauce
  \item 15g sugar
\end{enumerate}

\header{Instructions}
\begin{enumerate}
  \item Mix the marinade ingredients together, then mix the marinade with the
  ground pork.
  \item Mix the sauce ingerdients to allow the sugar to dissolve.
  \item Cut all vegetables into thin slices.
  \item Heat up your wok, then fry the meat on low heat until lightly browned.
  \item
\end{enumerate}
