\chapter{Cookies and Biscuits}

\section{Savoiardi \label{Savoiardi}}
\header{Ingredients}
\begin{enumerate}
  \item 2 eggs
  \item 40g sugar
  \item 40g flour
  \item 20g starch
\end{enumerate}

\header{Instructions}
\begin{enumerate}
  \item Preheat your oven to 200C.
  \item Separate the yolks from the whites.
  \item Add sugar to the whites and whip until smooth and forms peaks.
  \item Whip the yolks until pale and foamy.
  \item Fold the yolks gently into the whites until homogenous.
  \item Incorporate the flour and the starch into the eggs so that no lumps
    remain.
  \item Fill a piping bag with the batter and pipe the fingers onto a parchment
    paper.
  \item Bake for ~7 minutes.
\end{enumerate}

\section{Oatmeal Cookies}
\header{Ingredients}
For about 18 cookies:
\begin{enumerate}
  \item 250g oatmeal
  \item 200g flour (type 450-650)
  \item 150g butter
  \item 2 eggs
  \item 4g salt
  \item 4g cinnamon
  \item dried fruits (for example cranberry)
  \item 100g 64\% chocolate or chocolate chips
  \item brown sugar, honey or caramel (optional)
  \item water (optional)
\end{enumerate}

\header{Instructions}
Preheat your oven to about 165C.

Take a steel pot and set it over medium heat. Add butter and brown until butter
solids appear and the liquid turns golden brown. It is important to transfer
the liquid butter to a bowl or another container, or cool the pot in a water
bath until it is around room temperature because otherwise the butter might
burn from the heat stored in the pot.

Blend half the oatmeal coarsely, transfer to a container, then blend the dried
fruits until they turn into tiny pieces. We do not want to turn them into a
paste, though. Cut the chocolate int rough 5mm squares.

Take a large bowl and mix eggs and sugar. Add butter and mix until combined,
then add flour and whisk until the mass turns smooth. Add your remaining
ingredients and mix until the mass is uniform. If the mass is crumbly, add some
water.

Line a baking tray with parchment paper. Scoop a small portion of the dough,
form into a rough ball, then lay on the tray and press down until about 1cm
thick. Repeat to make 9 cookies. Bake for 17 minutes or until the bottom of the
cookies is brown.
